%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
  {Machine Learning Engineer} % Job title
  {Vaultree} % Organisation
  {Dublin, Ireland} % Location
  {Oct 2024 - Current} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and maintained a GCP-hosted Jupyter Notebook demo environment using Terraform and Docker.}
      \item {Integrated cloud services including HashiCorp KMS and GCP Buckets via API for secure data handling in private demos.}
      \item {Designed and published an open-source Python library integrating Rust using Maturin and PyO3; automated builds with GitHub Actions.}
      \item {Implemented CI tools such as Black and Ruff, and generated project documentation automatically.}
      \item {Built CUDA-based cryptographic primitives from academic papers (FHE), including NTT and Hybrid Relinearisation.}
      \item {Bridged Rust and Python using \texttt{rust-bindgen}, \texttt{ctypes}, and \texttt{nvcc}; developed and benchmarked proof-of-concept pipelines.}
      \item {Created unit and integration tests to ensure system reliability and correctness.}
      \item {Planned and managed the development roadmap for a novel ML library leveraging FHE, CUDA, and Rust.}
      \item {Represented the engineering team in external partnership calls and technical discussions.}
    \end{cvitems}
  }

\cventry
  {Data Analyst} % Job title
  {Allied Irish Banks (AIB)} % Organisation
  {Dublin, Ireland} % Location
  {Sept 2020 - Sept 2022} % Date(s)
  {
    \begin{cvitems}
      \item {Managed Teradata Data Warehouse and Microsoft SQL Server databases.}
      \item {Designed and built ETL pipelines to generate risk assessments and regulatory reports.}
      \item {Supported system upgrade and migration projects for data infrastructure.}
      \item {Performed A/B testing and resolved data quality issues through root-cause analysis.}
      \item {Replicated errors and validated data workflows using SSMS and Excel pivot tables.}
      \item {Integrated CI/CD practices with JIRA and custom version control systems.}
      \item {Worked in both Agile and Waterfall development lifecycles.}
      \item {Liaised with stakeholders to translate business requirements into technical specifications.}
      \item {Created and maintained internal documentation on Confluence.}
      \item {Mentored three new hires, assisting with onboarding and training.}
    \end{cvitems}
  }

\cventry
  {Research Intern - \href{https://github.com/marcohoucheng/Research-in-Latent-Position-Models}
  {github.com/marcohoucheng/Research-in-Latent-Position-Models}} % Job title
  {University College Dublin} % Organisation
  {Dublin, Ireland} % Location
  {June 2019 - Aug 2019} % Date(s)
  {
    \begin{cvitems}
      \item {Conducted research on Latent Position Models under the supervision of Dr. Riccardo Rastelli.}
      \item {Simulated social network models in R using Markov Chain Monte Carlo methods.}
      \item {Applied Game Theory and Bayesian Risk Theory to compare and optimise statistical models.}
      \item {Optimised algorithms to reduce computational overhead and improve model performance.}
    \end{cvitems}
  }

\cventry
  {Leaving Certificate Tutor} % Job title
  {Private Tutor} % Organisation
  {Dublin, Ireland} % Location
  {Sept 2017 - June 2019} % Date(s)
  {
    \begin{cvitems}
      \item {Tutored both Ordinary and Higher Level Mathematics for the Leaving Certificate.}
      \item {Taught Higher Level Applied Mathematics as an extra-curricular subject.}
      \item {Developed customised academic strategies based on individual student needs.}
      \item {Prepared weekly lesson plans and liaised with parents on student progress.}
    \end{cvitems}
  }

\end{cventries}