%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
%---------------------------------------------------------
  \cventry
    {\href{https://github.com/marcohoucheng/Brain-Tumor-Segmentation-with-Computer-Vision}{github.com/marcohoucheng/Brain-Tumor-Segmentation-with-Computer-Vision}} % Organisation
    {Brain Tumour Segmentation Prediction} % Project
    {} % Location
    {Feb 2024 - Apr 2024} % Date(s)
    {
        \begin{cvitems} % Description(s) of project
            \item {A pipeline computer vision deep learning model with a Convolutional-Autoencoder and a U-Net model.}
            \item {Identify the region and segmentation of brain tumours through MRI scans.}
            \item {Achieved a test accuracy of 98\%.}
            \item {\textbf{Technical Skills:} Python with Pytorch, cv2, pandas, multiprocessing libraries}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/marcohoucheng/ML-Interpreter}{github.com/marcohoucheng/ML-Interpreter}} % Organisation
    {Meta Functional Language Interpreter} % Project
    {} % Location
    {Oct 2022 - Jan 2023} % Date(s)
    {
        \begin{cvitems} % Description(s) of project
            \item {Built an interpreter for a meta functional language following theoretical type inference and evaluation rules.}
            \item {Implemented with a type inference mechanism to ensure absolute type safety within expressions.}
            \item {Developed comprehensive understanding of the functioning of programming language compilers.}
            \item {\textbf{Technical Skills:} F\#, functional languages}
        \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {\href{https://github.com/marcohoucheng/Gran-Turismo-7-Price-Tracker}{github.com/marcohoucheng/Gran-Turismo-7-Price-Tracker}} % Organisation
    {Gran Turismo 7 Price Tracker} % Project
    {} % Location
    {Dec 2023 - Mar 2024} % Date(s)
    {
        \begin{cvitems} % Description(s) of project
            \item {Aimed to create a solution without the requirement of creating accounts on existing services.}
            \item {Automated email service to notify dynamic in-game information updates in HTML format.}
            \item {Streamlined process to create and update local databases with a scheduled web-scraper.}
            \item {\textbf{Technical Skills:} Python with pandas, urllib, smtplib, ssl and more}
        \end{cvitems}
    }
    
%---------------------------------------------------------

  \cventry
    {\href{https://github.com/marcohoucheng/Computer-Vision-and-Deep-Learning}{github.com/marcohoucheng/Computer-Vision-and-Deep-Learning}} % Organisation
    {Computer Vision and Deep Learning Projects} % Project
    {} % Location
    {Aug 2023 - Dec 2024} % Date(s)
    {
        \begin{cvitems} % Description(s) of project
            \item {A series of Python Notebooks showcasing studies of various computer vision and deep learning topics.}
            \item {Models implemented including SIFT, Bag of Words, CNN, Recurrent Neural Networks, LSTM, GRU, Transformers and more.}
            \item {Utilising pre-trained models such as AlexNet, GoogLeNet and ResNet.}
            \item {\textbf{Technical Skills:} Python with Pytorch, pandas, cv2 and more}
        \end{cvitems}
    }

%---------------------------------------------------------


\end{cventries}